---
title: "Exponential Distribution in R Compared Against Central Limit Theorem"
output: pdf_document
---

## Overview

In a few (2-3) sentences explain what is going to be reported on.

## Simulations

Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.

```{r}
averageSampleMeans <- NULL
sampleVariances <- NULL
for (i in 1 : 1000) {
  expDist <- rexp(40, 0.2)
  averageSampleMeans = c(averageSampleMeans, mean(expDist))
  sampleVariances = c(sampleVariances, var(expDist))
}
```

## Sample Mean versus Theoretical Mean

Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.

Distribution of 1000 averages of 40 exponential distributions:
```{r}
hist(averageSampleMeans)
```

## Sample Variance versus Theoretical Variance

Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.

Sample variance is
```{r}
hist(sampleVariances)
```

## Distribution

Via figures and text, explain how one can tell the distribution is approximately normal. 

```{r}
hist(rnorm(1000, sqrt(mean(sampleVariances)), sd(averageSampleMeans)))
```